Sample Distribution Testing

### 2021-06-22 Sample Distribution Testing.Rmd
implemented and tested a function that calculates the cosine similarity between a vector of mutations and mutational signature matrix

polE.sample.vector <- create_signature_sample_vector(polE, 1000)
polE.sample.vector

@@

```

>>>>

polE.sample.vector <- create_signature_sample_vector(polE, 1000)
polE.sample.vector
#function that calculates the cosine similarity between the vector of mutations and a signature matrix
signature_cosine_similarity(polE.sample.vector, polE)

@@
